Exponential Integrals\\ [1ex]

### 2022-02-17 draft2.tex
Include whole thimble in 3/2-derivative argument
Also make some stylistic changes. Feel free to revert those!

\begin{equation}
I(z)\defeq\int_{\mathcal{C}}e^{-zf}\nu
\end{equation}
where $\mathcal{C}$ is a suitable countur such that the integral is well defined.  
For any Morse cirtial points $x_\alpha$ of $f$, the saddle point approximation gives the following formal series 
\begin{equation}
I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n} \qquad \text{ as } z\to\infty
\end{equation}
where $\mathcal{C}_\alpha$ is a steepest descendet path through the critical point $x_\alpha$. 
\begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$ and assume $f''(x_\alpha)\neq 0$ for every critical point $x_\alpha$. Then
\begin{enumerate}
\item $\tilde{\varphi}_\alpha$ is Gevrey-1;
\item $\hat{\varphi}(\zeta)\defeq\mathcal{B}(\tilde{\varphi})$ is a germ of analytic function at $\zeta=\zeta_{\alpha}=f(x_\alpha)$;
\item the following formual holds true
\begin{multline}\label{formula1}
\hat{\varphi}_{\alpha}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta, \text{based at }\zeta_\alpha}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)=\Gamma(-1/2)\int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2}\textcolor{red}{\partial_{\zeta'}\left(\int_{f^{-1}(\zeta')}\frac{\nu}{df}\right)} d\zeta'
\end{multline} 
\end{enumerate}
\end{theorem}
\begin{proof}
Part $(1)$: Let us assume that locally $\nu=\sum_{j\geq 0}b_j^{\alpha}(t-t_{\alpha})^{j}dt$ for $|t-t_\alpha|<\varepsilon$. By the steepest descendet method, $I_\alpha(z)$ can be aproximated as $z\to\infty$ as
\begin{align*}
I_\alpha(\zeta)&\sim e^{-zf(x_\alpha)}\int_{-\varepsilon}^{\varepsilon}\sum_{n\geq 0}t^{2n}b_{2n}^{\alpha}e^{-zf''(x_\alpha)\frac{t^2}{2}}dt\\
&=e^{-zf(x_\alpha)}\sum_{n\geq 0}b_{2n}^{\alpha}\int_{-\varepsilon}^{\varepsilon}t^{2n}e^{-zf''(x_{\alpha})\frac{t^2}{2}}dt\\
&=\sqrt{2\pi}e^{-zf(x_\alpha)}z^{-1/2}\sum_{n\geq 0}\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!! z^{-n}\mathrm{Erf}\left(\frac{\sqrt{z f''(x_\alpha)}}{\sqrt{2}}\varepsilon\right)+\\
&-2e^{-zf(x_\alpha)}\sum_{n\geq 1}b_{2n}^{\alpha}(2n-1)!!e^{-zf''(x_{\alpha})\frac{\varepsilon^2}{2}}\sum_{j=1}^n\frac{\varepsilon^{2j-1}}{(2j-1)!!}\left(f''(x_\alpha)z\right)^{n-j+1}\\
&\sim_{\varepsilon<<1} 2\varepsilon \sqrt{2\pi}e^{-zf(x_\alpha)}z^{-1/2}\sum_{n\geq 0}\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!! z^{-n}
\end{align*} 
therefore \[a_{\alpha,n}\defeq 2\varepsilon\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!!\]

@@

Part $(2)$: \begin{align*}
\hat{\varphi}_\alpha(\zeta)=\mathcal{B}\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
(2\pi)^{1/2} \left(\delta(f_{x_\alpha}) a_0+\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}\right)
\end{align*}
Since $a_{n}\leq CA^nn!$, the series $\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}$ has a finite radius of convergence.

Part $(3)$: thanks to properties of Caputo's fractional derivatives, we have that the Borel transform of $\tilde{I}_{\alpha}(z)=z^{-1/2}\tilde{\varphi}_\alpha(z)$ is 
\begin{equation}
\partial^{1/2}_{\zeta, \text{based at }\zeta_\alpha}\hat{I}_{\alpha}(\zeta)=\hat{\varphi}_{\alpha}(\zeta).
\end{equation} 
In addition, we notice 
\begin{align*}
I_{\alpha}(z)&=\int_{\mathcal{C}_{\alpha}}e^{-zf}\nu & f=\zeta\\
&=\int_{\mathcal{H}_{\alpha}}e^{-z\zeta}\partial_{\zeta}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)d\zeta   & \mathcal{H}_{\alpha} \text{ is Hankel countour} \\
&=:\int_{\mathcal{H}_{\alpha}}e^{-\zeta z}\hat{I}_{\alpha}(\zeta)d\zeta &
\end{align*}
hence 
\begin{equation}
\hat{\varphi}_{\alpha}(\zeta)=\partial^{1/2}_{\zeta, \text{based at } \zeta_\alpha}\left(\partial_{\zeta}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)\right)=\partial^{3/2}_{\zeta, \text{based at } \zeta_\alpha}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)
\end{equation}
\end{proof}

@@

\begin{multline}
\label{4.5}
\int_0^x |y|^{a-\mu-1}{}_2F_1\left(a,b;c,y\right)(x-y)^{\mu-1}dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{a-1}{}_2F_1\left(a-\mu,b;c;x\right)\\
x\in(-\infty,0)\cup(0,1), \, \Re a>\Re\mu>0
\end{multline}
which can be rewritten as 
\begin{multline}
\label{4.8}
\int_{y>x}|y|^{-a}|x-y|^{\mu-1}{}_2F_1\left(a,b;c;y^{-1}\right)dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{-a+\mu}{}_2F_1\left(a-\mu,b;c;x^{-1}\right)\\
x\in(-\infty,0)\cup(1,\infty), \, \Re a>\Re\mu>0
\end{multline}
%\textcolor{red}{We should check that for Hypergeomtric functions the following relation holds true
%\[{}_2F_1(a,b;c;z-1)\propto\int_1^z(z-t)^{-1/2}\left[{}_2F_1\left(a+\frac{1}{2},b+\frac{1}{2};c+\frac{1}{2};1-t\right)-{}_2F_1\left(a+\frac{1}{2},b+\frac{1}{2};c+\frac{1}{2};t\right)\right]dt\]
%}
%
%The following identities hold true
%\begin{multline}
%\label{a+b+c+}
%\int_{0<\frac{y}{x}<1}|y|^{c-1}(1-y)^{a+b-c}{}_2F_1\left(a,b;c;y\right)\frac{|x-y|^{\mu-1}}{\Gamma(\mu)}dy=\\
%\frac{\Gamma(c)}{\Gamma(c+\mu)}|x|^{c-1+\mu}(1-x)^{a+b-c+\mu}{}_2F_1\left(a+\mu,b+\mu;c+\mu;x\right)\\
% x\in (-\infty,0)\cup(0,1), \,\Re c>0,\,\Re\mu>0
%\end{multline}
%
%\begin{multline}\label{a-b-c-}
%\int_{-\infty}^x{}_2F_1\left(a,b;c;y\right) (x-y)^{\mu-1}dy=\Gamma(\mu)\frac{\Gamma(a-\mu)}{\Gamma(a)}\frac{\Gamma(b-\mu)}{\Gamma(b)}\frac{\Gamma(c)}{\Gamma(c-\mu)}{}_2F_1\left(a-\mu,b-\mu;c-\mu;x\right)\\
%x<1, \Re a,\Re b>\Re\mu>0
%\end{multline}

>>>>

\begin{equation}
I(z)\defeq\int_{\mathcal{C}}e^{-zf}\nu
\end{equation}
where $\mathcal{C}$ is a suitable countur such that the integral is well defined.  
For any Morse cirtial points $x_\alpha$ of $f$, the saddle point approximation gives the following formal series 
\begin{equation}
I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n} \qquad \text{ as } z\to\infty
\end{equation}
where $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$. Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha + [0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
\begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$ and assume $f''(x_\alpha)\neq 0$ for every critical point $x_\alpha$. Then:
\begin{enumerate}
\item The series $\tilde{\varphi}_\alpha$ is Gevrey-1.
\item The series $\hat{\varphi}(\zeta)\defeq\mathcal{B}(\tilde{\varphi})$ converges near $\zeta=\zeta_{\alpha}$.
\item For any $\zeta$ on the ray going rightward from $\zeta_\alpha$, we have
\begin{align*}\label{formula1}
\hat{\varphi}_{\alpha}(\zeta) & = \partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha}\left(\int_{\mathcal{C}_\alpha(\zeta)} \nu \right) \\
& = \Gamma\big(-\tfrac{1}{2}\big)\int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2}\textcolor{red}{\partial_{\zeta'}\left(\left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta')}^{\operatorname{end} \mathcal{C}_\alpha(\zeta')} \right)}\,d\zeta',
\end{align*}
where $\mathcal{C}_\alpha(\zeta)$ is the part of $\mathcal{C}_\alpha$ that goes through $f^{-1}([\zeta_\alpha, \zeta])$. Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
\end{enumerate}
\end{theorem}
\begin{proof}
Part~(1): Let us assume that locally $\nu=\sum_{j\geq 0}b_j^{\alpha}(t-t_{\alpha})^{j}dt$ for $|t-t_\alpha|<\varepsilon$. By the steepest descent method, $I_\alpha(z)$ can be aproximated as $z\to\infty$ as
\begin{align*}
I_\alpha(\zeta)&\sim e^{-zf(x_\alpha)}\int_{-\varepsilon}^{\varepsilon}\sum_{n\geq 0}t^{2n}b_{2n}^{\alpha}e^{-zf''(x_\alpha)\frac{t^2}{2}}dt\\
&=e^{-zf(x_\alpha)}\sum_{n\geq 0}b_{2n}^{\alpha}\int_{-\varepsilon}^{\varepsilon}t^{2n}e^{-zf''(x_{\alpha})\frac{t^2}{2}}dt\\
&=\sqrt{2\pi}e^{-zf(x_\alpha)}z^{-1/2}\sum_{n\geq 0}\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!! z^{-n}\mathrm{Erf}\left(\frac{\sqrt{z f''(x_\alpha)}}{\sqrt{2}}\varepsilon\right)+\\
&-2e^{-zf(x_\alpha)}\sum_{n\geq 1}b_{2n}^{\alpha}(2n-1)!!e^{-zf''(x_{\alpha})\frac{\varepsilon^2}{2}}\sum_{j=1}^n\frac{\varepsilon^{2j-1}}{(2j-1)!!}\left(f''(x_\alpha)z\right)^{n-j+1}\\
&\sim_{\varepsilon<<1} 2\varepsilon \sqrt{2\pi}e^{-zf(x_\alpha)}z^{-1/2}\sum_{n\geq 0}\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!! z^{-n}
\end{align*} 
therefore \[a_{\alpha,n}\defeq 2\varepsilon\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!!\]

@@

Part~(2): \begin{align*}
\hat{\varphi}_\alpha(\zeta)=\mathcal{B}\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
(2\pi)^{1/2} \left(\delta(f_{x_\alpha}) a_0+\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}\right)
\end{align*}
Since $a_{n}\leq CA^nn!$, the series $\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}$ has a finite radius of convergence.

Part~(3): thanks to properties of Caputo's fractional derivatives, we have that the Borel transform of $\tilde{I}_{\alpha}(z)=z^{-1/2}\tilde{\varphi}_\alpha(z)$ is 
\begin{equation}
\partial^{1/2}_{\zeta \text{ from }\zeta_\alpha}\hat{I}_{\alpha}(\zeta) = \hat{\varphi}_{\alpha}(\zeta).
\end{equation}
%%Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_\alpha$ that go from the past to $x_\alpha$ and from $x_\alpha$ to the future, respectively. Noticing that $f \circ \mathcal{C}^\pm_\alpha$ are both injective, we can recast the integral $I_\alpha$ into the $f$ plane.
%%\[ I_{\alpha}(z) = \int_{\mathcal{C}^-_{\alpha}} e^{-zf} \nu + \int_{\mathcal{C}^+_{\alpha}} e^{-zf} \nu \]
Let's recast the integral $I_\alpha$ into the $f$ plane. Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_\alpha$ that go from the past to $x_\alpha$ and from $x_\alpha$ to the future, respectively. As $\zeta$ goes rightward from $\zeta_\alpha$, the start and end points of $\mathcal{C}_\alpha(\zeta)$ sweep backward along $\mathcal{C}^-_\alpha(\zeta)$ and forward along $\mathcal{C}^+_\alpha(\zeta)$, respectively. Hence, we have
\begin{align*}
I_\alpha(z) & = \int_{\mathcal{C}_{\alpha}} e^{-zf} \nu \\
& = \int_{\zeta_\alpha}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}\,d\zeta.
\end{align*}
Noticing that the right-hand side is a Laplace transform, we learn that
\[ \hat{I}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}. \]
Observing that
\[ \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}, \]
we conclude that
\[ \hat{I}_\alpha(\zeta) = \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right)\,d\zeta. \]
Hence
\begin{align*}
\hat{\varphi}_{\alpha}(\zeta) & = \partial^{1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha \\
& = \partial^{3/2}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right)\,d\zeta.
\end{align*}
\end{proof}

@@

\begin{multline}
\label{4.5}
\int_0^x |y|^{a-\mu-1}{}_2F_1\left(a,b;c,y\right)(x-y)^{\mu-1}dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{a-1}{}_2F_1\left(a-\mu,b;c;x\right)\\
x\in(-\infty,0)\cup(0,1), \, \Re a>\Re\mu>0
\end{multline}
which can be rewritten as \textbf{(\texttt{arXiv:1504.08144}, formula~4.8)}
\begin{multline}
\label{4.8}
\int_{y>x}|y|^{-a}|x-y|^{\mu-1}{}_2F_1\left(a,b;c;y^{-1}\right)dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{-a+\mu}{}_2F_1\left(a-\mu,b;c;x^{-1}\right)\\
x\in(-\infty,0)\cup(1,\infty), \, \Re a>\Re\mu>0
\end{multline}
%\textcolor{red}{We should check that for Hypergeomtric functions the following relation holds true
%\[{}_2F_1(a,b;c;z-1)\propto\int_1^z(z-t)^{-1/2}\left[{}_2F_1\left(a+\frac{1}{2},b+\frac{1}{2};c+\frac{1}{2};1-t\right)-{}_2F_1\left(a+\frac{1}{2},b+\frac{1}{2};c+\frac{1}{2};t\right)\right]dt\]
%}
%
%The following identities hold true
%\begin{multline}
%\label{a+b+c+}
%\int_{0<\frac{y}{x}<1}|y|^{c-1}(1-y)^{a+b-c}{}_2F_1\left(a,b;c;y\right)\frac{|x-y|^{\mu-1}}{\Gamma(\mu)}dy=\\
%\frac{\Gamma(c)}{\Gamma(c+\mu)}|x|^{c-1+\mu}(1-x)^{a+b-c+\mu}{}_2F_1\left(a+\mu,b+\mu;c+\mu;x\right)\\
% x\in (-\infty,0)\cup(0,1), \,\Re c>0,\,\Re\mu>0
%\end{multline}
%
%\begin{multline}\label{a-b-c-}
%\int_{-\infty}^x{}_2F_1\left(a,b;c;y\right) (x-y)^{\mu-1}dy=\Gamma(\mu)\frac{\Gamma(a-\mu)}{\Gamma(a)}\frac{\Gamma(b-\mu)}{\Gamma(b)}\frac{\Gamma(c)}{\Gamma(c-\mu)}{}_2F_1\left(a-\mu,b-\mu;c-\mu;x\right)\\
%x<1, \Re a,\Re b>\Re\mu>0
%\end{multline}
